What We Eval in the Shadows

### 2021-08-11 paper/main.tex
Fix table 8 and table 9
Fix table
Fix figures so they do not end up at the end
Update 5.4

\begin{figure}[!b]
\centering
  \includegraphics[width=10cm]{pkgs-eval-callsites-hist.pdf}
  \caption{ \eval call sites}\label{fig:pkgs-eval-callsites-hist}

@@

\begin{wraptable}{r}{7cm}\small\centering
  \begin{tabular}{lrrrr}\toprule
    \bf Environments & \bf \#sites & \bf \%sites & \bf \#funs. & \bf \%funs. \\%
    \expandableinput tag/table-se-target-envs.tex
  \end{tabular}
  \caption{Target environments for side-effects} \label{tab:se-env}
\end{wraptable}

@@

\begin{table}[h]
  \small
  \centering
  \begin{tabular}{lrrrrrr}\toprule
    \bf Side effect & \bf \#events & \bf \%events & \bf \#calls & \bf \%calls & \bf \#sites & \bf \%sites \\%
    \expandableinput tag/table-se-types.tex
  \end{tabular}
  \caption{Types of \eval side-effects} \label{tab:se-types}
\end{table}

Out of the minimized expressions, it is \c{BLOCK}, \c{<-} and
\c{F(F(X)} that contribute to the vast majority of side effects. Concretely,
92\% of \c{BLOCK}, 87\% of \c{<-} and 15\% of \c{F(F(X))} expressions contain
side effects. In the case of \c{BLOCK}, most of the side effects happen in the
environment passed to \eval (which by default is the parent environment, \ie
the local or function in our classification). For \c{<-} it is 15\%, however,
that is only because of the \c{plyr::allocate\_column} which does the side
effect in the environment containing the data frame that is the target for the
newly allocated column. Without this call, \c{<-} is similarly predictable with
96\% of side effects in the passed environment. For \c{F(F(X))} minimization
for, it is less clear as 48\% of side effects happen in a different environment
to the one that was passed to \eval.

>>>>

\begin{figure}[!b]
\centering
  \includegraphics[width=9cm]{pkgs-eval-callsites-hist.pdf}
  \caption{ \eval call sites}\label{fig:pkgs-eval-callsites-hist}

@@

\begin{wraptable}{r}{7cm}\small\centering
  \begin{tabular}{lrrrr}
    \toprule
    \bf Environments & \bf \#sites & \bf \%sites & \bf \#funs. & \bf \%funs. \\%
    \midrule
    \expandableinput tag/table-se-target-envs.tex
    \bottomrule
  \end{tabular}
  \caption{Target environments for side-effects} \label{tab:se-env}
\end{wraptable}

@@

\begin{table}[h]
  \small
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    \bf Side effect & \bf \#events & \bf \%events & \bf \#calls & \bf \%calls & \bf \#sites & \bf \%sites \\%
    \midrule
    \expandableinput tag/table-se-types.tex
    \bottomrule
  \end{tabular}
  \caption{Types of \eval side-effects} \label{tab:se-types}
\end{table}

Out of the minimized expressions, it is \c{BLOCK}, \c{<-} and \c{F(F(X)} that
contribute to the vast majority of side effects. Concretely, 92\% of \c{BLOCK},
87\% of \c{<-} and 15\% of \c{F(F(X))} expressions do side effects. In the case
of \c{BLOCK}, most of them happen in the environment passed to the \eval call
(default is the parent environment). For \c{<-} it is 15\%. However, this form
is dominated by the \c{plyr::allocate\_column} function that side-effects in
the environment containing the data frame to which it allocates new column.
Without this call, \c{<-} is similarly predictable with 96\% of side effects
happening in the passed environment. For \c{F(F(X))}, it is less clear as 58\%
of side effects happen in a different environment to the one that was passed to
\eval.
